\LARGE \bf Children Teach a Robot to Write: A Teachable Robotic Agent which Engages in Simulated Handwriting

### 2014-12-07 main.tex
First draft of previous robotics work

The \emph{learning by teaching} paradigm, which engages the target student in
the act of teaching another, has been shown to produce motivational,
meta-cognitive, and educational benefits in a range of disciplines
\cite{Rohrbeck2003}. The application of the paradigm to handwriting intervention
is previously unexplored. One reason for this may due to the requirement of 
an appropriately unskilled peer for the target child to tutor, which may present
a logistical constraint if the target child is the lowest performer in their class. 
In some cases, it may be appropriate for a
peer or teacher to simulate a na\"ive learner for the target child to teach.
For handwriting, where one's skill level is visually evident, however, 
this acting is likely to be eventually detected. As such,
there is motivation for the use of a teachable agent which can be configured for
a variety of skill levels, and for which children do not have preconceptions
about its handwriting ability.

@@

%this part will be rearranged once prev work is involved:
The teachable agent developed has the potential to be embedded as a simulated 
computer-based agent, however there are three main points which have motivated 
the use of a robot instead as the teachable agent in the presented work:

\begin{enumerate}
    \item the engagement and ``protégé effect'' elicited by teaching an embodied
        agent is anticipated to be stronger than that associated with a
        tablet-based application, which children are increasingly recognising as
        disposable technology,% * <deanna.m.hood@gmail.com> 2014-09-08T11:07:10.004Z:
%
% ... citation needed?
%

    \item observing a teachable agent respond to what it has been taught
        is a significant step in the learning by teaching
        paradigm \cite{Okita2006}, and therefore it may be significant for the agent to respond
        with a physical writing \emph{process}, rather than simply a product, and

    \item the potential for motor mimicry to yield significant improvements in
        handwriting interventions in which letter formations are demonstrated to participants \cite{Berninger1997} further supports the case
        for investigating the use of a humanoid robot capable of physically
        demonstrating handwriting trajectories to its child learning partner.
\end{enumerate}

Consequently, the learning agent developed has been embodied in a commercially
affordable {\sc nao} humanoid robot. Its writing capabilities have been implemented by
leveraging synchronisation with a tablet display to simulate fine motor skills
otherwise infeasible for the robot.

>>>>

The \emph{learning by teaching} paradigm, which engages the target student in
the act of teaching another, has been shown to produce motivational,
meta-cognitive, and educational benefits in a range of disciplines
\cite{Rohrbeck2003}. The application of the paradigm to handwriting intervention
is previously unexplored. One reason for this may due to the requirement of 
an appropriately unskilled peer for the target child to tutor, as this may present
a logistical constraint if the target child is the lowest performer in their class. 
In some cases, it may be appropriate for a
peer or teacher to simulate a na\"ive learner for the target child to teach.
For handwriting, where one's skill level is visually evident, however, 
this acting is likely to be eventually detected. As such,
there is motivation for the use of a teachable agent which can be configured for
a variety of skill levels, and for which children do not have preconceptions
about its handwriting ability.

@@

Teachable computer-based agents have previously been used to encourage the 
``protégé effect'', wherein students invest more effort into learning when it
is for a teachable agent than for themselves \cite{Chase2009}. As we are 
concerned with learning of a physical skill, the learning agent developed has 
been embodied in a humanoid robot which is capable of physically demonstrating 
handwriting trajectories to its child learning partner.
This is supported by the potential for motor mimicry to yield significant 
improvements in handwriting interventions in which letter formations are 
demonstrated to participants \cite{Berninger1997}.

A robotic learning agent which employs the learning by teaching paradigm has 
previously been developed by Tanaka and Matsuzoe \cite{Tanaka2012}. In their
system, children learn vocabulary by teaching the {\sc nao} robot to act out 
verbs. The robot is tele-operated and mimics the actions that the children
teach it, but with no long-term memory or learning algorithm in place.
Our work instead focuses on an autonomous robotic partner which the child 
can teach a physical skill.
This differs from the established work of robots learning physical skills
from demonstrations, which has focused exclusively on
the robot learning physical skills for the benefit of the robot -- to play table 
tennis, for example -- not the human teacher \cite{Werfel2014}.

%Indeed, as a commercially affordable robot is being used, the handwriting that
%it engages in is in fact emph{simulated}, for interaction purposes, by 
%leveraging synchronisation with a tablet display. Hence the system does not 
%have, nor does it depend on, capabilities to improve its physical skills for
%its own benefit.

Due to the intended use in a school environment, a commercially
affordable {\sc nao} humanoid robot has been used. Its writing capabilities 
have been implemented by leveraging synchronisation with a tablet display to
simulate fine motor skills otherwise infeasible for the robot.
